\textbf{ Accurate spectrophotometric estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-07-26 paper/sp.tex
outline tweaks

\author{Hans-Walter Rix}
\affiliation{Max-Planck-Institut f\"ur Astronomie}

@@

We take the \gaia\ data and apply the parallax offset.

@@

Brief comment on the flexibility of the photometric model.

We do 2-fold train-and-test to make results independent of \gaia.

@@

>>>>

\author[0000-0003-4996-9069]{Hans-Walter Rix}
\affiliation{Max-Planck-Institut f\"ur Astronomie}

@@

HOGG: We take the \gaia\ data and apply the parallax offset.

@@

HOGG: We do 2-fold train-and-test to make results independent of \gaia.

@@

Brief comment on the flexibility of the photometric model and interpretation of the photometric coefficients. Maybe plot some photometric properties vs metallicity or dust?
